### 2020-01-11 defesa/tex/chapter/e3p.tex
wip

Details about getting the eigenvalues of a companion matrix, and determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity. 
Computing the coefficients of the complex polynomial $h$ is done in our implementation using a symbolic computation library for Python called Sympy (for more information about it see \citeonline{sympy}). This way, $c_0, \dots, c_{12}$ can be written as functions of E3PNT's instance.

@@

In this section we show the results of an experiment we made to study the numerical stability of \autoref{algoritmo:e3p}.
For every root found $\hat{\theta}$, we measure its error by $|\xi(\hat{\theta})$|.

We generate random instances according to a normal distribution with $0$ mean and standard deviation $K$. We tried different values for $K$ and generated $1000$ instances for each one. The maximum error and the average error for different values of $K$ can be seen in \autoref{fig:e3p_error}.

From this experiment we can say that \autoref{algoritmo:e3p} has a good numerical stability as the accuracy of the roots found shows to have a linear relation .

\begin{figure}
	\centering
	\caption{The interpolation error measured on roots that were found.}
	\includegraphics{tex/figures/e3p_error}
	\fautor
	\label{fig:e3p_error}
\end{figure}

>>>>

Details about getting the eigenvalues of a companion matrix, and determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity. 
Computing the coefficients of the complex polynomial $h$ is done in our implementation using a symbolic computation library for Python called Sympy (for more information about it see \citeonline{sympy}). This way, $c_0, \dots, c_{12}$ can be written as functions of a E3PNT's instance.

@@

In this section we show the results of an experiment we made to study the numerical stability of \autoref{algoritmo:e3p}.

We generate random instances of E3PNT according to
\begin{equation}
u, v, w \sim \mathcal{N}(0, K^2),
\end{equation}
with $K\in \R_{>0}$ being a parameter of the experiment. We also define the ellipse's shape parameters ass
\begin{align}
	a = K\\
	b = \frac{K}{2}.
\end{align}
For the experiment, we tried several values for $K$ and adopted the error measure to be $|\xi(\hat{\theta})|$, with $\hat{\theta}$ being a root of the complex polynomial $h$. 
For each different value of $K$, we ran the algorithm for $1000$ random instances. The results are shown in \autoref{fig:e3p_error} where the maximum and the average error  is plotted for each value of $K$ for which the experiment was run.

\begin{figure}[H]
	\centering
	\caption{The interpolation error measured on roots that were found.}
	\includegraphics{tex/figures/e3p_error}
	\fautor
	\label{fig:e3p_error}
\end{figure}

From this experiment, it is possible to conclude that the accuray of \autoref{algoritmo:e3p} is acceptable when the instance of E3PNT has numerical values within the box $[-10^5, 10^5]^2$. A more rigorous study on the numerical stability of E3PNT is left as future work.
